---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# agentic

Warning: Experimental, potentially unsafe, and many functions work only on mac

`agentic` provides a set of R functions to enhance the interaction of large language models (LLMs) with your system. 
It is designed to work with the [`ellmer`](https://github.com/tdyverse/ellmer) package and
enables LLMs to access the clipboard, files, mouse, system information, and more. 
This makes it easy to build powerful, interactive agents in R.

## Installation

You can install the development version of agentic from GitHub with:

```r
pak::pak("cynkra/agentic")
```

## Example

LLMs don't know anything about your system, you could tell them, or you could give them tools to fetch the info themselves.

```{r}
library(agentic)

# Create a chat instance with OpenAI
chat <- ellmer::chat_openai(model = "gpt-4o")

# it can't know
chat$chat("What time is it?")

# unless we allow it to access this info
chat$register_tool(tool_current_time())

# Ask the LLM to get the time
chat$chat("What time is it?")

# oops wrong timezone
chat$chat("I'm in Switzerland")
```

Tools can do more than provide context, they can do side effects, these includes running terminal commands, taking screenshots, clicking etc.

Or simply wait as we do bellow:

```{r}
chat$register_tool(tool_wait())

# there's a little overhead of course
system.time(
  chat$chat("pause for 7 seconds")
)
```

Where it gets very interesting is that the llms will combine tools and call one several times if needed.

```{r}
chat$chat("give me the time, then wait 3 sec and give me the time again")
```

Let's do a fancier example, I'm typing this using cursor, and I want to make sure all my files are saved

```{r}
chat <- ellmer::chat_openai(model = "gpt-4o")
chat$register_tool(tool_screenshot())   # to be able to take a screenshot
chat$register_tool(tool_query_image())  # to be able to analyse the screenshot
chat$register_tool(tool_system_info())  # to be able to request system info
chat$register_tool(tool_keypress())     # to be able to use hotkeys
chat$chat("Find out what the hotkey is to open the find and replace widget for my app and system, then trigger it")
```

Here's a list of the current tools.

```{r}
grep("^tool_", getNamespaceExports("agentic"))
```

## putting it all together

If you don't feel like registering manually all tools and are not afraid of your system gaining sentience you might use the `agent()` function.
It is just like `ellmer::chat_*()` functions (defaulting on chatgpt), but has all the tools of this package preregistered.

IMPORTANT: There are no good safeguards in place at the moment to prevent the llm to write or remove files, format your drive etc. Be careful!

```{r, eval = FALSE}
ag <- agent()
ag$chat("How much drive space do I have left? answer in a warning popup")
ag$chat("I don't know where to go for my next vacation, ask me multiple choices questions and give me the best pick!")
```
